---
title: "r-debenture"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparing the Environment

### Libraries

#### pdftools

`pdftools` (see: <https://ropensci.org/blog/2016/03/01/pdftools-and-jeroen/>)

Requires OS dependency install:

```
sudo apt-get install libpoppler-cpp-dev
```

#### alphavantage

`alphavantage4` (see: https://www.business-science.io/code-tools/2017/09/03/alphavantager-0-1-0.html)

```
install.packages("alphavantager")
library(alphavantager)
av_api_key("YOUR_API_KEY")
print(av_api_key())
```
Get the key from the environment with `Sys.getenv("ALPHAVANTAGE_KEY")` and put the environment variables in `~/.Renviron`

```
av_get(symbol = "MSFT", av_fun = "TIME_SERIES_INTRADAY", interval = "15min", outputsize = "compact")
```

## Appendix

### Library Management

Library dependencies are installed with the `install.packages()` command and by default results in in the library package being placed in `/home/gheinze/R/x86_64-pc-linux-gnu-library/3.4/`

```
install.packages("pdftools")
```

The package could be explicitly loaded into another location:

```
install.packages("pdftools", lib="~/r-library")
```

The `Rprofile.site` allows global configuration of the R environment.  The following line could be added to extend the `libPaths`:

```
.libPaths( c( "~/r-library", .libPaths() ) )
```

To determine location of the `Rprofile.site`, query R directly:

```
gheinze@gheinze-t410 ~ $ R RHOME
/usr/lib/R

gheinze@gheinze-t410 ~ $ R
> Sys.getenv("R_HOME")
[1] "/usr/lib/R"
```

Alternatively, for non-global configuration, set the environment variable `R_LIBS_USER` to the libPaths.

By default, the library is pulled from the `CRAN` repository.


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
